Efficient Community Formation \\ for Web Services

### 2014-01-20 papers/coalition-journal-R1/response_letter-final.tex

%\documentclass[preprint,authoryear,12pt]{elsarticle}
\documentclass[times, 12pt,a4paper]{article}
\usepackage{graphicx,amssymb,amsthm,stmaryrd}%,booktabs}
\usepackage{times}
\usepackage{amsmath,url,algorithm,algorithmic,mathrsfs,makeidx}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsfig}
\usepackage{latex8}

%journal{Journal of Knowledge-Based Systems}

\begin{document}
%\begin{frontmatter}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary} {Corollary}
\title{\underline{Response Letter}\\\vspace{0.5cm}Efficient Community Formation for Web Services}
\author{Ehsan Khosrowshahi Asl\\
e\_khosr@encs.concordia.ca\\
\and
Jamal Bentahar\\
bentahar@ciise.concordia.ca \\
\and
Hadi Otrok\\
hadi.otrok@kustar.ac.ae \\
\and
Rabeb Mizouni\\
rabeb.mizouni@kustar.ac.ae \\
}

\maketitle

First, we would like to thank and express our appreciation to the
reviewers for taking the time to carefully review our manuscript,
and for their insightful, valuable, and very useful comments. We
would like to thank the associate and chief editors as well for
their valuable comments and suggestions for improvements. We
carefully considered the comments and implemented all of them in
the revised version. In this letter, we will explain, point by
point, how the issues raised in the reviews are addressed and
answered. We hope our answers and revisions will satisfy the
reviewers and editors, which will make the paper accepted for
publication in IEEE Transactions on Services Computing (TSC).\\

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 1 %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
  \textbf{Reviewer 1}
\end{center}

\vspace{0.6cm} \textbf{\underline{Reviewer's appreciation}:} The
paper presents a nice modelling of community formation based on
coalition games. The authors defended well their approach and
provided good illustrative examples.

\vspace{0.2cm}\textbf{\underline{Answer}: Thank you for the
positive feedback.}

\vspace{0.5cm} \textbf{\underline{1. Reviewer}:} Page 4: Last
paragraph: should be $x_i$ instead of $i$ at the condition level.

\vspace{0.2cm}\textbf{\underline{Answer 1}: Thanks for the
comment. Actually, the confusion comes from Equation 2, which
should be $\forall S \subseteq N, \sum_{i \in S} x_i \geq v(S)$
instead of $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)$
as $x_i$ is the payoff vector of the player $i$ and $S$ is the set
of all players. This has been fixed in Equation 2 and Equation 4
as well (Section 2.4).}

\vspace{0.5cm}\textbf{\underline{2. Reviewer}:}  Page 6: You
should relate $v(S)$ to $PO(C)$ in equations 5 and 6.

\vspace{0.2cm}\textbf{\underline{Answer 2}: The connection between
$v(S)$ and $PO(C)$ has been mentioned in Section 3.3, second
paragraph and when we described the algorithm of our scenario in
Section 4.1. To be more specific, the connection is between $v(C)$
and $Out(C)$ that is computed in Equation 6 based on $PO(C)$
computed in Equation 5. The connection is that the worth of a
community is set to the output the community can generate, i.e.,
$v(C) = Out(C)$. However, we agree that this should be reported
earlier. In the revised version it is clearly stated just after
Equation 6 (Section 3.2). }
% RABEB: I do not get what you mean by however we had .... I beleive taht you need to reformulate your answer by saying that : The connection between V(S) to PO(C) has been already defined when describing the algorithm of our scenario in section 4.1. To clarify it more, we modified the section and we added the connection at the end of the paragraph.

\vspace{0.5cm}\textbf{\underline{3. Reviewer}:} Page 7: Please add
some definitions such as the one for Grand coalition to make the
paper self-contained.

\vspace{0.2cm}\textbf{\underline{Answer 3}: In the revised
version, all the needed concepts are defined. Grand coalition is
defined as follows: In cooperative game theory, grand coalition is
a coalition that contains a maximum number of players as long as
they can maintain a stable (in terms of membership) and beneficial
(in terms of utility) group for all the players (Section 4.1,
paragraph 3).}

\vspace{0.5cm}\textbf{\underline{4. Reviewer}:} Why you didn't
leverage the foundations of repeated games instead of coalitional
games? Is there any strong reason?.

\vspace{0.2cm}\textbf{\underline{Answer 4}: The main objective of
this work is to optimize the gain of web service communities as a
whole and to ensure the creation of stable communities in terms of
joining and leaving activities. Such a problem is formulated by
the means of coalition games, a part of cooperative game theory
where the gain can be fairly distributed based on the contribution
of each member using the theory of \emph{shapley value}. In this
context, communities can be formed and have their stability
condition formulated based on the \emph{Core} solution concepts.
Repeated games fit better in situations where web services are
competing with each other so they can learn the best response by
playing the game repeatedly. In our case, web services are rather
cooperating where the objective of web services communities is to
motivate intra-community cooperation and to motivate quality web
services to join such communities. Because each community is seen
as a cooperative group where members cooperate to achieve a better
outcome, cooperative game theory methods provide us with great
decision mechanisms for forming groups and coalitions which would
benefit the agents involved altogether.}

\textbf{In fact, because members of the same community are
providing similar functionalities, one can argue that they are
competing with each other, rather than cooperating. However, the
main idea, and also the main innovation and contribution of the
paper is to show that those member web services can form strong
and stable communities as coalitions so that they can better
compete as a whole with other web services and other communities,
which will allow them to be better off. In other words, we are
promoting the idea of intra-community cooperation and
inter-community competition. This justifies the use of coalition
games instead of repeated games.}

\textbf{Because we found it important as motivation of our choice
of coalition games, this discussion is reflected in the revised
version in the introduction section (Section 1, Motivations part).
In this new part, we added examples from the business world to
highlight the cooperation strategy. This has been raised by
Reviewer 3 as well (see additional details in our Answer 1 to
Reviewer 3).}

%In repeated games, there should be a repeatable game between agents one to one. The  decision cannot be optimal for all the agents involved. We believe repeated game is more appropriate in cases where there is a lot of competing one-to-one interactions between agents  happening and not in coalitions.
 %and actually we are working on repeated games and specifically repeated game with learning techniques such as q-learning to help distribute the ``task distribution job'' among all the web services where web services are having different confidence states, and based on their action history and state they are in, web services can directly opt for getting and performing tasks alone or cooperating which other agents.
% RABEB: I do not see the need for the last sentence starting from and actually we are as you are opening the door for questioning our decision  ...

\vspace{0.5cm}\textbf{\underline{5. Reviewer}:} Page 8: What do
you mean by "the algorithm gets interrupted": is it based on a
logical condition? if yes, what is it?

\vspace{0.2cm}\textbf{\underline{Answer 5}: The interruption we
are mentioning can be either caused by time/memory constraints
when the number of subsets is big enough (timeout) or forced
manually by the system designer if for example the already
obtained results are satisfactory. In fact, if the algorithm gets
interrupted while verifying $depth(n)$, it will have $depth(n-1)$
already verified. Each depth will have $O(n^2)$ cases to check, so
for example if it reaches depth 10, and the algorithm gets
interrupted (manually or because of system resources), we at least
have checked for all the subsets of depth 9. Clarification has
been added in the revised manuscript at Section 4.1, last
paragraph.}

\vspace{0.5cm}\textbf{\underline{6. Reviewer}:} Page 9: Please
provide equations using $\lambda$ and $\epsilon$ and relate them
to your model that uses $R_C$.

\vspace{0.2cm}\textbf{\underline{Answer 6}: Thanks for this
suggestion. We added in the revised version the following equation
Equation 8 (Section 4.3, paragraph 2) linking the Shapley value of
a web service $i$ when moving from one community $C$ to another
one $C'$ to $\epsilon$.
%
\begin{equation*}\label{eq:gainsh}
g_i(C \rightarrow C') = \phi_i(C',v) - \phi_i(C,v) - \epsilon
\end{equation*}
%
It relates our model that uses $R_C$ and $\epsilon$ as the Shapley
value is computed using $v(C)$, which in turn is computed using
$Out(C)$ based on $R_C$. The idea is that before deciding to
change the community (from $C$ to $C'$), each web service $i$ has
to be sure that the gain $g_i(C \rightarrow C')$ calculated based
on the Shapley values of $i$ in the previous and new communities
and the tax $\epsilon$ is positive, which means, what the web
service would gain in $C'$ is greater than what it gains in $C$
and the tax it would pay if moving all together. Furthermore, we
added in paragraph 3 of the same section (Section 4.3) the
following linear program that determines the minimum value of
$\lambda$ that makes the community stable ($Core$ condition):
%
 \begin{alignat*}{3}
    \min~   & \lambda  \\
    \text{s.t. } & \lambda v(C) > v(C') & ~& \text{ for all } C' \subset C
  \end{alignat*}
%
}

\vspace{0.5cm}\textbf{\underline{7. Reviewer}:} Page 10: For the
$\epsilon$ core method: the value of $\epsilon$ should be varied
to verify its impact in the experiments section.

\vspace{0.2cm}\textbf{\underline{Answer 7}: Yes, the value of
$\epsilon$ should vary to verify its impact and that is exactly
what we are doing in our experiments. In the revised manuscript,
we changed the explanation to make this fact more clear: Section
5, paragraph 5. See also Fig. 5}

\vspace{0.5cm}\textbf{\underline{8. Reviewer}:} The experiments
are missing a comparison with [18].

\vspace{0.2cm}\textbf{\underline{Answer 8}: The experiment
illustrated in Figure 9 (Last paragraph of Section 5) presents a
comparison of our work with [18]. We have called their method
``High Availability Coalition model''. We highlight this in the
new caption of this figure.}

\vspace{0.5cm}\textbf{\underline{9. Reviewer}:} Scalability
evaluation is missing: what is the impact of increasing the number
of services/communities on the system efficiency?.

\vspace{0.2cm}\textbf{\underline{Answer 9}: We conducted
scalability tests. We used 10,000 communities consisting of 3 to
160 web services. This number is large enough since in the
concrete examples of coalitions in the airlines domain we are
implementing, the largest coalition, Star
Alliance\footnote{\url{www.staralliance.com}}, has 28 airline
members. When conducting our experiments using the real web
service data provided in
\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}, in
average, the communities were populated by 60 web services. Thus,
in total, the number of used web services is 600,000. This makes
our system scalable enough. We also conducted experiments with a
large number of tasks from users up to 130 per iteration per
community, which means 6500 (130*50) tasks per community. We
observed that increasing the number of communities and web
services did not affect the overall efficiency of the system in
terms of coalition formation. In fact, as mentioned in the paper,
our algorithms run in $O(n)$ and $O(n^2)$ time as the number of
web services $(n)$ within a community grows. Thus, our algorithms
run in polynomial time. On the other hand, increasing the number
of tasks did not affect our results, since communities only accept
tasks at rate $R_C$. In the revised manuscript we highlighted the
runtime of our \emph{Depth-1 Convex-Checker} and \emph{Depth-2
Convex-Checker} methods in our experiments in Section 5, paragraph
4.}
%In case $R_C$ is set very large, communities can grow larger, and may suffer from  bottleneck due to huge number of task processing on a single server, a fact that is out of scope of this paper.

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 2 %%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2cm}

\newpage

\begin{center}
  \textbf{Reviewer 2}
\end{center}

\vspace{0.6cm} \textbf{\underline{Reviewer's appreciation}:} This
paper investigates into web services communities and the quality
of service in aggregating the web services in communities. The aim
is to maximize the efficiency through collaboration and through
forming coalitions of web services and improving the overall QoS
and revenue. The problem of web services community is interesting
as there exist a large number of web services with varying level
of QoS. The paper provides a good rationale behind the use and
establishment of communities of web services – esp. community web
services should be highly available and responsive; maintain
collaboration with others as well as maintain their own autonomy,
when used in business or any other settings.

The paper reviews the current work on web service communities and
QoS and identifies their strengths and weaknesses. It then
exploits the game theory approach and proposes a cooperative game
model for the aggregation of web services within communities. The
proposed model is well designed and developed. It’s also logically
mapped to the characteristics of web services they exhibit in
communities.

The proposed model is implemented as a prototype system and
various simulation experiments are conducted. The experimental
results show the benefits of the proposed model in terms of
stability, fairness, increase in revenue and in improvement of
user satisfaction.

Overall, the paper is well written and well structured.

\vspace{0.2cm}\textbf{\underline{Answer}: Thank you for the
positive feedback.}

\vspace{0.5cm}\textbf{\underline{1. Reviewer}:}  Though there's a
referral to [8] it'd be helpful to explain more the concept of
``Community coordinators'' web services, somewhere in the early
parts of the paper. How's it different from other (common) web
services in a given community?

``community master'' and ``community coordinator'' are these
different?

\vspace{0.2cm}\textbf{\underline{Answer 1}: First, there is no
difference between community master and community coordinator. To
avoid the confusion, we only use in the revised version the term
``community coordinator'' as community manager for our
architecture; ``community master'' has been kept only when it is
used as such in the literature. Second, we agree on your
suggestion and added the following explanation in Section 1,
paragraph 2: When communities are used, users send their requests
to the coordinators of those communities, which play the role of
their representatives or access points. Community coordinator is a
particular service that takes in charge the verification of
credentials of new web services before accepting them to join the
community, inviting good web services to join the community,
firing bad web services if they don't perform as expected, etc.
The coordinator is responsible for all the operations related to
the management of the community infrastructure in terms of
regulating the membership and insuring that the overall
performance is satisfactory. Unlike web services that are members
of the community, the coordinator does not offer services directly
to the users, it only forwards the requests to the suitable
members. The coordinator is created by the community owner when
the community is initiated.}

\vspace{0.5cm} \textbf{\underline{2. Reviewer}}: p.4 ``If he is
added to the set $S$,…'', ``his contribution…'' not sure `he' and
`his' are the right terminologies.

\vspace{0.2cm}\textbf{\underline{Answer 2}: We agree, we rephrased
the sentence as follows:  If the member $i$ is added to the set
$S$, the contribution of this set to the coalition is $v(S \cup
\left\{i\right\}) - v(S)$.}

\vspace{0.5cm} \textbf{\underline{3. Reviewer}}: p.10 ``our
community receives 130 tasks from users'' what are the types of
tasks. Are these simulated or real functions that need to
performed by web services?

\vspace{0.2cm}\textbf{\underline{Answer 3}: In the previous
version, the tasks were abstract. In the revised version, the
tasks are real tasks about flight booking that need to be
performed by web services. The users provide the flight dates, the
origin and destination, type of tickets, and number of guests. Web
services will find different flights with different companies,
prices, timing, etc. During our experiments, the tasks are
randomly generated and are coded as XML requests (String) and
responses are also coded in XML. Based on community task queue
delay and the assigned web service quality metrics (such as
reliability, throughput, latency and other metrics) these tasks
will be performed with different qualities. In the experimental
results and analysis section (Section 5), we have illustrated and
evaluated the average QoS of tasks performed. In the revised
manuscript, we added more explanations and details about the tasks
in Section 5. Other details are also mentioned in our Answer 5 to
Reviewer 3.}

\vspace{0.5cm} \textbf{\underline{4. Reviewer}}: p.9 “agents would
only earn a minimal amount of e by deviating….” …by deviating from
what?

\vspace{0.2cm}\textbf{\underline{Answer 4}: We mean deviating from
the coalition. This has been fixed in the revised version.}

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 3 %%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2cm}

\newpage

\begin{center}
  \textbf{Reviewer 3}
\end{center}

\vspace{0.6cm}\textbf{\underline{1. Reviewer}:}  It is not
convincing that the formation of service community can be modeled
as a cooperative gaming problem.

### 2014-01-20 papers/coalition-journal-R1/coalition_journal_r1-final.tex
changes

\usepackage{amsfonts}
\usepackage{amssymb,amsmath}
 \usepackage{comment}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide web services with better
visibility, efficiency, market share and total payoff. A number of
mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities.
However, forming optimal and stable communities as coalitions to
maximize individual and group efficiency and income is yet to be
addressed. In this paper, we propose an efficient community
formation mechanism using cooperative game-theoretic techniques,
particularly Shapley value, core, $\epsilon$-core and convex
games. We propose a mechanism for community membership requests
and selections of web services under two scenarios: (1) there is
only one community and many web services aim to join it; and (2)
web services can join different established communities. The
ultimate objective is to develop a mechanism for web services to
form stable groups allowing them to maximize their efficiency and
generate near-optimal (welfare-maximizing) communities where a
taxation-based solution is being proposed. The theoretical and
extensive simulation results show that our algorithms provide web
services and community owners, in real-world-like environments,
with applicable and near-optimal decision making mechanisms.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

\section{Introduction and Related Work}

@@

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings
\cite{YuB13,Younas2012,LiuBWZ13}. The idea of grouping web
services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar or
complementary functionalities \cite{Zeng:2003:QDW:775152.775211,
Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7},
but probably different non-functional quality attributes, which
form the QoS parameters. When communities are used, users send
their requests to the masters of those communities, which are
responsible of managing the communities, forwarding the requests
to the suitable member web services and checking the credentials
of those members. Communities aim to provide higher service
availability and performance than what individual web services can
do. The high availability of services and the community resilience
to failure are guaranteed since web services can cooperate and
replace each other within the same community and since there is no
single point of failure in the communities architecture.

@@

\textbf{Web Service Community.}
Communities of web services are a collection of web services with same functionality sharing a
coordinator or service broker as manager which also serves as the access point to the community. Web service communities facilitate the discovery of web services and also provide services with better quality.

As an example, let us consider major air liners providing ticket selling service. We can consider them as competing agents, which each try to maximize their utilities by gaining more of the market share. However, major airliners, can collaborate if the collaboration would be beneficial for \emph{all} the agents. By sharing resources and also market share and also having the option of service multi-hop air tickets combined from different air liners, both air liners can increase their gain by collaborating. The question is when this collaboration would be beneficial for all the agents involved? For example major airliners would not gain anything by collaborating and sharing resources with airliners of low reputation and quality. They will lose their market and would rather stay away from this collaboration, therefore no stable cooperation can form between them.

In \cite{DBLP:journals/internet/BenatallahSD03}, Behatallah et al. defined communities as \emph{Service Containers} which aggregates substitutable web services providing a common functionality (same set of operations). They abstracted \emph{Service Containers} as web services which are created, advertised, discovered and invoked just as elementary web services, they \emph{Container} as a manager is responsible for the mentioned tasks and also web service selection upon receiving a request on run-time. They have proposed a scoring service based on non-functional requirement of the task and web service capabilities to dynamically chose the web service to perform the task upon receiving requests. A similar concept was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}. They introduced web service communities as a collection of web services with a common functionality but different QoS properties. A community manager upon receiving a request, delegates the request to one of its current members. The choice is based on history and quality metrics of each web service. They have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requires aggregation of different type of services to satisfy a request.

Benslimane et al. \cite{Liris-2770} have proposed a multi-layer approach, grouping similar Web services into communities and having an interface implemented as an abstract Web service for accessing the community on top of the community layer. The interactions between composite, management and community layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC).

Authors in \cite{managing-hela-jalel} have proposed web service communities with centralized access across distributed web services. They have proposed a framework for web service management, query resolution among communities and a query caching mechanism to improve the performance of query resolution process among many distributed communities by caching previous computed results for answering future queries.

Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities of web services.

This architecture has been further developed in
\cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10,
conf/aina/LimTM11, CSTintercommunity}. Two types of roles have
been distinguished for community members: masters and slaves.
Master web services lead communities and are responsible for
membership management. They can invite and convince slave web
services to join the community, and attract new slave web services
to their communities by awarding them better payoff. Moreover,
they can eject some slave members from the community to improve
its overall reputation if these members are misbehaving or cannot
provide the promised QoS \cite{DBLP:journals/ijebr/MaamarSTBB09}.

In \cite{Medjahed05adynamic} authors developed a community as a ``container'' that clusters Web services based on a specific area of interest. All web services in a given community, share the same functionality. These communities are created by \emph{third party community providers} which use the \emph{community ontology} as a template and define a set of operations that all web services within a community should provide. Using semantic analysis on web service operations, web services either find and join a community with similar functionality or create a new operation description for a new community.

The rest of the paper is organized as follows. Section
\ref{s:preliminaries} describes the architecture, considered
parameters and some basic cooperative game theory concepts.
Section \ref{s:model} provides the problem statement and some
numerical examples for illustration. Section \ref{s:game_solution}
presents our solution model in two different scenarios. Section
\ref{s:resutls} describes our experiments and results. Finally,
Section \ref{s:conclusion} concludes the paper and identifies
future work.

@@

\emph{1) Web services} are rational entities\footnote{The term
rational is used here in the sense that web services are utility
maximizers} providing services to end users. They aim to maximize
their individual income by receiving enough requests from end
users. In order to increase their revenue, web services seek for
more tasks if they have the capacity and throughput to do so. Web
services can join communities to have better efficiency by
collaborating with others, to have access to higher market share,
and to have opportunity of receiving a bigger task pool from end
users. Throughout this paper, in our equations, we refer to web
services as $ws$ and to the set of web services hosted by a given
community as $C$. To simplify the notation, sometimes we simply
write $ws$ instead of $ws \in C$ to go through the elements $ws$
of the set $C$, when $C$ can be understood from the context.

@@

\begin{figure*}[!t]
\centerline{\includegraphics[width=6.25in]{community.eps}}
\caption{Architecture of web service communities}
\label{fig_community}
\end{figure*}

>>>>

\usepackage{amsfonts,url}
\usepackage{amssymb,amsmath}
 \usepackage{comment}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide web services with better
visibility, efficiency, market share and total payoff. A number of
mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities.
However, forming optimal and stable communities as coalitions to
maximize individual and group efficiency and income is yet to be
addressed. In this paper, we propose an efficient community
formation mechanism using cooperative game-theoretic techniques,
particularly Shapley value, core, $\epsilon$-core and convex
games. We propose a mechanism for community membership requests
and selections of web services under two scenarios: (1) there is
only one community and many web services aim to join it; and (2)
web services can join different established communities. The
ultimate objective is to develop a mechanism for web services to
form stable groups allowing them to maximize their efficiency and
generate near-optimal (welfare-maximizing) communities where a
taxation-based solution is being proposed. The theoretical and
extensive experimental results show that our algorithms provide
web services and community owners, in real-world-like
environments, with applicable and near-optimal decision making
mechanisms.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

\section{Introduction}\label{s:introduction}

@@

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings
\cite{YuB13,Younas2012,LiuBWZ13}. The idea of grouping web
services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar or
complementary functionalities \cite{Zeng:2003:QDW:775152.775211,
Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7},
but probably different non-functional quality attributes, which
form the QoS parameters. Web service communities facilitate the
discovery of web services and also provide services with better
quality. When communities are used, users send their requests to
the coordinators of those communities, which play the role of
their representatives or access points. A community coordinator is
a particular service that takes in charge the verification of
credentials of new web services before accepting them to join the
community, inviting good web services to join the community,
firing bad web services if they do not perform as expected, etc.
The coordinator of a community is responsible for all the
operations related to the management of that community
infrastructure in terms of regulating the membership and insuring
that the overall performance is satisfactory. Unlike web services
that are members of the community, the coordinator does not offer
services directly to the users, it only forwards the requests to
the suitable members. The coordinator is created by the community
owner when the community is launched. Communities aim to provide
higher service availability and performance than what individual
web services can do. The high availability of services and the
community resilience to failure are guaranteed since web services
can cooperate and replace each other within the same community and
since there is no single point of failure in the communities
architecture.

\textbf{Motivations.} Communities of web services are then
collections of functionally similar autonomous web services
sharing a coordinator or service broker as manager which also
serves as the access point to the community. In this paper, we
advocate the idea of community as a way to group web services in
order to increase the total gain of all the members where each web
service gain is more than or equal to what this web service would
obtain being outside the community. This is because the community
can provide wider visibility, better market share, higher
reputation, and better way of sharing resources. Community is an
infrastructure and being part of it should benefit the web
service, but also the community as a whole.

As argued in \cite{CSTintercommunity}, members of a web services
community can either compete or cooperate. In this paper, we
stress the intra-community cooperation (i.e., among members of the
same community) for a better inter-community competition. The main
idea is that to form a stable community in terms of membership and
to have fair distribution of the total gain among the individual
members based on their contributions, cooperative game theory,
particularly the part of coalition games, provides a very suitable
framework. For instance, we cannot leverage the theory of repeated
games as a way to model the problem, because such a theory is
suitable for situations where web services are competing with each
other so they can learn the best response by playing the game
repeatedly. In fact, it has been proved that cooperation among
competitors is an effective business model
\cite{Chetty2003,Bucklin1993}. Several concrete examples in the
businesses world are following this model such as coalitions among
competitive airlines and coalitions in the automobile sector. For
the first example, three large and well known coalitions, called
alliances, are very active, namely Star
Alliance\footnote{\url{www.staralliance.com}} (includes 28 airline
members), SkyTeam\footnote{\url{www.skyteam.com}} (has 19
members), and Oneworld\footnote{\url{ www.oneworld.com}} (groups
13 members). Airlines of the same community are competing because
each one tries to maximize its utility by gaining more market
share. However, by sharing resources and market share and having
the option of service multi-hop air tickets combined from
different airlines, each airline member of a coalition can
increase its gain by collaborating. For the second example, the
coalition among PSA Peugeot Citro\"{e}n and Toyota that creates
Toyota Peugeot Citro\"{e}n Automobile
(TPCA)\footnote{\url{www.tpca.cz/en/}} has been very successful.
This coalition allowed the three competitors to share components
for a new city car while saving money on shared costs. Our model
of cooperation between competitor web services as coalitions
within communities follows these business models. The key question
we address is when such collaborations would be beneficial for all
the agents involved? For example the three airline alliances would
not gain anything by collaborating and sharing resources with
airlines of low reputation and quality. They will lose their
market and would rather stay away from this collaboration.
Therefore, no stable community can be formed between well
established and poor airlines.

Web services in the same community are independent and autonomous.
They are self-interest and utility maximizer agents, and behave
autonomously towards maximizing their own profits using our game
theory approach. They have the freedom to leave the community
anytime if they are not satisfied about the profit they are
making. Having a community manager, only means that the management
of the community infrastructure in terms of accepting new web
services and verifying the credentials of the members is
centralized. In other words, the coordinator does not manage web
services, but does manage the community. The manager does not
dictate what the web services should do and how they should
behave. In fact, because the community is an infrastructure that
hosts different web services, membership cannot be leaved open so
that any web service can join even those having poor quality and
bad reputation. A community is a system that should accept only
particular web services, and there should be a mechanism to
control the credentials of the members. In the real case of
airlines, the three aforementioned alliances are managed by
centralized entities:
%
\begin{itemize}
%
\item Star Alliance is managed by a centralized company \emph{Star
Alliance Services
GmbH}\footnote{\url{www.staralliance.com/en/about/organisation/}};
%
\item SkyTeam has centralized core management team, \emph{SkyTeam
Central}\footnote{\url{http://www.skyteam.com/en/About-us/Organization/Management/}};
and
%
\item Oneworld is managed by its central alliance office, the
\emph{Oneworld Management Company}
(\emph{oMC})\footnote{\url{www.oneworld.com/news-information/oneworld-fact-sheets}}.
%
\end{itemize}
%
In all these alliances, accepting a new member or pending a member
is decided centrally. Regarding the second example, TPCA coalition
is also managed by a central management company based Czech
republic\footnote{\url{www.tpca.cz/en/about-us/management-tpca-en-us/}}.

\textbf{Organization.} The rest of the paper is organized as
follows. Section \ref{s:related-work} discusses relevant related
work. Section \ref{s:preliminaries} describes the architecture,
considered parameters and some basic cooperative game theory
concepts. Section \ref{s:model} provides the problem statement and
some numerical examples for illustration. Section
\ref{s:game_solution} presents our solution model in two different
scenarios. Section \ref{s:resutls} describes our experiments and
results. Finally, Section \ref{s:conclusion} concludes the paper
and identifies future work.

\section{Related Work}\label{s:related-work}

In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} which aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services which are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager which is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
approach grouping similar Web services into communities and having
an interface implemented as an abstract web service for accessing
the community on top of the community layer. The interactions
between composite, management and community layers and the
bindings are performed by a generic driver called Open Software
Connectivity (OSC).

In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
service communities with centralized access across distributed web
services. They have proposed a framework for web service
management, query resolution among communities and a query caching
mechanism executed by the manager to improve the performance of
query resolution process among many distributed communities. The
key idea is to cache previous computed results for answering
future queries.

Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities of web
services. The protocol is centrally executed by the community
manager. This architecture has been further developed in
\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
roles have been distinguished for community members: masters and
slaves. Master web services and community managers that lead
communities and are responsible for membership management. They
can invite and convince slave web services to join the community,
and attract new slave web services to their communities by
awarding them better payoff. Moreover, they can eject some slave
members from the community to improve its overall reputation if
these members are misbehaving or cannot provide the promised QoS.

In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
developed a community as a ``cluster'' that groups Web services
based on a specific area of interest. All web services in a given
community share the same functionality. These communities are
created by \emph{third party community providers} which use the
\emph{community ontology} as a template and define a set of
operations that all web services within a community should
provide. Using semantic analysis on web service operations, web
services either find and join a community with similar
functionality or create a new operation description for a new
community. The authors have described the concept of
\emph{community agents} associated to \emph{community providers}.
A community agent is responsible, among other things, of the
registration of services with the community. An example of a
community that provides health care services to senior citizens
has been used. In this example, a governmental entity is needed to
check the health care standards used by the members before
authorizing them to be part of the community. Such a central
entity is represented by the community agent. Thus, community
agents are playing the role of community managers. In a close work
\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
global planning selection algorithm and a delegation algorithm to
be run when a request to execute an operation is received by the
community. This needs a central entity to run those algorithms.
Such entity plays the same role as the community coordinator or
manager.

@@

@@

\emph{1) Web services} are rational entities\footnote{The term
rational is used here in the sense that web services are
autonomous and utility maximizers} providing services to end
users. They aim to maximize their individual income by receiving
enough requests from end users. In order to increase their
revenue, web services seek for more tasks if they have the
capacity and throughput to do so. Web services can join
communities to have better efficiency by collaborating with
others, to have access to higher market share, and to have
opportunity of receiving a bigger task pool from end users.
Throughout this paper, in our equations, we refer to web services
as $ws$ and to the set of web services hosted by a given community
as $C$. To simplify the notation, sometimes we simply write $ws$
instead of $ws \in C$ to go through the elements $ws$ of the set
$C$, when $C$ can be understood from the context.

@@

\begin{figure*}%[!t]
\centerline{\includegraphics[width=6.25in]{community.eps}}
\caption{Architecture of web service communities}
\label{fig_community}
\end{figure*}
